Parallel Algorithms for the Probabilistic Roadmap Method for Robotic Motion Planning with GPU Acceleration

### 2016-07-27 paper/paper.tex
stand besprechung ..

\title{ Parallelization of the Probabilistic Roadmap Method with GPU Acceleration}
%\subtitle{High Performance Computing Project}
%\date{}
\author{Manuel Demmeler \and Manfred Liebmann}

\institute{Manuel Demmeler
\at todo ... \\ 
\email{manuel.demmeler@yahoo.de}
\and
Manfred Liebmann
\at todo ... \\  %TODO: which adresses to use?
\email{todo}
}

@@

\section{Abstract}
In trajectory optimization with obstacles, it is often necessary to provide feasible initial trajectories. 
For example in robot motion planning, where the dimensions of the underlying spaces are rather high, this can be expensive. A further problem is that because of the transformation from work into configuration space, the obstacles are often no longer given in a closed form. An efficient approximative solution for this is using probabilistic roadmaps (PRMs).

In this paper, a parallelized version of the PRM method has been developed in general.
A robotics application then was implemented as an special case of this with GPU support.

>>>>

\journalname{Journal of Intelligent \& Robotic Systems}
\title{ Parallel Algorithms for the Probabilistic Roadmap Method for Robotic Motion Planning with GPU Acceleration}
%\subtitle{High Performance Computing Project}
%\date{}
\author{Manuel Demmeler \and Manfred Liebmann}

\institute{Manuel Demmeler
\at todo ... \\ 
\email{manuel.demmeler@yahoo.de}
\and
Manfred Liebmann
\at Technische Universität München\\
%Chair of Optimal Control,
Center for Mathematical Sciences, M17 \\
Boltzmannstraße 3,
85748 Garching by Munich \\  %TODO: which adresses to use?
\email{manfred.liebmann@tum.de}
}

@@

\begin{abstract}
In trajectory optimization with obstacles for robot motion planning, it is often necessary to provide feasible initial trajectories. 
For example in robot motion planning, where the dimensions of the underlying spaces are rather high, this can be expensive. 
A further problem is that because of the transformation from work into configuration space, the obstacles are often no longer given in a closed form. 
An efficient approximative solution for this problem is the probabilistic roadmap method (PRM).
In this paper, a parallelized version of the PRM method has been developed in general.
A robotics application then was implemented as a special case of this with GPU support.
\keywords{probabilistic roadmap method \and robot motion planning \and parallel algorithms \and GPU acceleration}
\end{abstract}
